---
title: "Group Member Evaluation Form"
author: "Brian Vuong"
date: today
format: html
---

## Group Member Evaluation Form

**Instructions:**
Please evaluate your group members (including yourself) on a scale of 1 to 100%.

- If a member contributed equally to the group project, give them 100%
- If a member did not do their fair share, assign a percentage less than 100%
- Evaluation will be confidential
- If a member receives grades less than 100% from more than one person, the average of peer evaluations will be weighted to their individual grade
- Each student must evaluate peers in the absence of other members to guarantee confidentiality
- Submit your completed form directly to the instructor in a sealed envelope marked "confidential"
- Identify the group leader (MVP) if applicable—they may receive up to 10% bonus

---

## Evaluation Table

```{r}
#| label: setup
#| include: true

# Create a data frame to store peer evaluations
evaluation_data <- data.frame(
  member_number = 1:5,
  member_name = c("Brian (Self)", "Ron", "Alexa", "Kevin", "Sandy"),
  grade_percent = c(100, 100, 100, 100, 100),
  is_mvp = c("No", "Yes", "No", "No", "No")
)

# Display the evaluation table
library(knitr)
kable(evaluation_data, 
      col.names = c("Member #", "Member Name", "Grade (%)", "MVP (Yes/No)"),
      caption = "Group Member Evaluation Scores")
```

---

## Submission Instructions

**Name:** Brian V

**Date:** July 17

**Group Name/Project Name:** Proposal Presentation for Farm Store Client

## Peer Evaluation

In the table above, provide the following information for each group member (including yourself):

1. **Member Name:** Enter the name of each group member
2. **Grade (%):** Assign a percentage from 1-100%
3. **MVP (Yes/No):** Check only ONE person if you believe they were the group leader/MVP

---

## Comments Section

Please provide brief comments on the contributions of your teammates to the project. If you gave anyone a grade less than 100%, please justify your evaluation below.

```{r}
#| label: comments
#| eval: false

# Contribution summary
contributions <- "
Brian (Self): Worked on Business Objective

Ron: Worked on Client Background and Project Objective

Alexa: Worked on Methods

Kevin: Worked on Timeline

Sandy: Worked on Mock Deliverables

All members contributed equally with 100% effort. Leeann was identified as the MVP for exceptional leadership and contribution to the project's success.
"

cat(contributions)
```
